\documentclass[12pt]{article}

%%Packages Used
\usepackage{xcolor} % for different colour comments
\usepackage[hidelinks]{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{float}
\usepackage{tabto}
\usepackage{longtable}
\usepackage{fullpage}
\usepackage{tabularx}

%% Comments
\newif\ifcomments\commentstrue
\ifcomments
\newcommand{\authornote}[3]{\textcolor{#1}{[#3 ---#2]}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\else
\newcommand{\authornote}[3]{}
\newcommand{\todo}[1]{}
\fi
\newcommand{\wss}[1]{\authornote{magenta}{SS}{#1}}
\newcommand{\ds}[1]{\authornote{blue}{DS}{#1}}
\newcommand{\kly}[1]{\authornote{green}{KL}{#1}}
\newcommand{\cc}[1]{\authornote{orange}{CC}{#1}}

%% Diagram formatting
\tikzstyle{block} = [draw, fill=blue!20, rectangle, minimum height=3em, minimum 
width=6em, text centered]
\tikzstyle{line} = [draw, -stealth', thick]
\tikzstyle{block2} = [draw, fill=blue!20, rectangle, minimum height=1em, minimum 
width=2em, text centered]
\tikzstyle{arrow} = [thick,-,>=stealth]
\tikzstyle{block3} = [draw, draw=black, fill=orange!20, rectangle, minimum 
height=3em, minimum width=6em, text centered]
\tikzstyle{block4} = [draw, draw=black, fill=green!20, rectangle, minimum 
height=3em, minimum width=6em, text centered]



 


\begin{document}

\title{Software Requirements Specifications for Quarters} 
\author{James Anthony (1135089)\\ Wenqiang Chen(1155437)\\ Carolyn Chong 
(1139105)\\ Kevin Ly (1144604)}
\date{\today}
\maketitle

\pagebreak

\tableofcontents 
\listoffigures
\listoftables

\section*{Revision History}
\begin{longtable}{|p{5cm}|p{10cm}|}
\hline
\textbf{Date}  & \textbf{Comments} \\ \hline
October 9, 2015 & Created first draft. \\ 
\hline
January 17, 2016 & Made some revisions based on marking feedback, including Other Stakeholders, Users of the Product, Constraints, Work Partitioning, Product Use Case Diagram, Nonfunctional requirements, and general spelling errors. \\ 
\hline
\end{longtable}

\section*{Template}
This document makes use of the Volere Template for all of its organization.

\pagebreak

\section{Project Drivers}
\subsection{The Purpose of the Project}
\subsubsection{Project Background}
Communication is the exchange of information between two parties. It is an important aspect of people's everyday lives. With the introduction 
of the Internet and cellular devices people's capacity to communicate has vastly 
improved, however, this information has hardly centralized. Landlords and their 
tenants commonly communicate via email, instant messaging or phone calls, but a response is not always guaranteed or the reply is hard to retrace. This lack of centralized 
communication may introduce confusion and frustration between the two parties in addition to challenges sharing documents and other important information.\\

\noindent Developing a new software platform to serve as an intermediate between 
landlords and tenants to act as a centralized hub of information will improve 
the quality of communication and create a more functional living environment 
for the occupants.

\subsubsection{Project Goal}
This platform is designed to handle information between landlords and their 
tenants, as well as between other tenants. It efficiently and systemically 
handles communication between all parties and gives a detailed status of the household.

\subsection{The Client, the Customer, and Other Stakeholders}
\subsubsection {The Client}
  N/A.
\subsubsection {The Customer}
This platform is designed for tenants and landlords. It provides tenants with the ability to communicate efficiently and effectively with each other and their landlord. The customer requires a robust, easy-to-learn platform.
\subsubsection {Other Stakeholders}
Other stakeholders whose input is needed to build the product include software developers to create and test the application, in addition to the project supervisor to provide guidance and advice on the design and implementation.
\subsection{Users of the Product}
There are two key users of the product: tenants and landlords. \\ \\
Tenants have the following role:
\begin{enumerate}
\item Communicate information to other tenants when needed
\item Complete the chores assigned to them
\item Report maintenance issues in the house via the ticketing system
\item Be punctual with payments
\item Ensure the rules outlined for the house are followed
\item 18+ years old
\item Basic web browsing experience required
\end{enumerate}
Landlords have the following role:
\begin{enumerate}
\item Communicate information regarding the house to the tenants
\item Respond to tenant questions and inquiries
\item Complete maintenance requests within a timely manner
\item Be available when issues arise
\item 18+ years old
\item Basic web browsing experience required
\end{enumerate}


\section{Project Constraints}
\ds{How are any of these constraints? Constraints are typically given by your client
	due to their existing technological infrastructure. These are all requirements.
	If these constraints have been mandated from the beginning, \emph{explain why}} 
	
\subsection{Solution Constraints}
\textbf{Constraint \#:} 1 \\
\textbf{Description: } The web application must run on an Intel i3-4430 server running Ubuntu. \\
\textbf{Rationale: } The team of developers already had access to this server. \\
\textbf{Fit Criterion: } The web application works on the server.

\subsection{Implementation Environment of the Current System}
N/A.

\subsection{Partner or Collaborative Applications} 
	\ds{Why are any of these constraints?}
    \begin{itemize}
    \item Facebook Login: Provides users with the option to sign up via Facebook.
    \item Google Sign-In: Provides users with the option to sign up via Google.
    \item PayPal Payments: Provides users with the option to make payments via PayPal. 
    \end{itemize}
    
\subsection{Off-the-Shelf Software} 
  \ds{Are you going to be using these exclusively? Why are you constrained to using them?}
    \begin{itemize}
    \item PostgreSQL: An object-relational database management system (ORDMBS)
      with an emphasis on extensibility and on standards-compliance.
    \item ExpressJS: A NodeJS web application server framework, designated for
      building single-page, multi-page, and hybrid web applications.
    \item AngularJS: An open-source web application framework.
    \item NodeJS: An open-source, cross-platform run-time environment for
      developing server-side web applications.
    \item Bootstrap: A free and open-source collection of tools for creating
      websites and web applications. 
    \end{itemize}
    
\subsection{Anticipated Workplace Environment} 
    \begin{itemize}
    \item Home: Website must display properly on desktop and laptop computers.
    \item Mobile: Website must display properly on mobile browsers. 
    \end{itemize}
    
\subsection{Schedule Constraints} 
    \begin{itemize}
    \item Proof of Concept Demonstration on November 24, 2015
    \item Revision 0 Demonstration, February 1-12
    \item Final Demonstration, Exam Period
    \end{itemize}
    
\subsection{Budget Constraints}
    N/A.
    
\subsection{Enterprise Constraints}
    N/A.

\section{Naming Conventions and Terminology}
    \begin{itemize}
    \item Landlord: A person who owns or runs a boarding house, inn, or similar
      establishment.
    \item Tenant: A person who occupies land or property rented from a landlord.
    \item House: In the context of this project, a house functions as a set
      which contains one or more users and stores information about the
      physical property, the users, and data added by those users.
    \item Maintenance request: A ticket created by a tenant to inform their
      landlord of property related maintenance that they are responsible for
      completing.
    \end{itemize}

\section{Relevant Facts and Assumptions} 
\subsection{Relevant Facts}
  \begin{itemize}
    \item Facebook Login is a secure form of account management.
    \item Google Sign-In is a secure form of account management.
    \item PayPal is a secure method of making online payments. 
  \end{itemize}
\subsection{Assumptions}
  \begin{itemize}
  \item  It is assumed that both landlords and tenants will be capable of using
    web applications for communication, planning, and payments.
  \end{itemize} 

\section{Functional Requirements} 
\subsection{The Scope of the Work}
\subsubsection{The Current Situation}
There is currently no existing software platform that attempts to simplify and 
document communication between landlords and tenants. A web application is 
needed to serve as a centralized management solution that will benefit both 
types of users. The web application will include document storage, in-app 
payment, a chore calendar, maintenance ticketing, instant messaging, and a 
discussion board.  
\subsubsection{The Context of the Work} 
See Figure \ref{fig:workcontext}.
\begin{figure}[H]
\centering
\begin{tikzpicture}[auto, node distance=4cm,>=latex']
% Place nodes
\node [block](user){User};  
\node [block, above of=user](webapp){Web Application};
\node [block, above of=webapp, yshift=2cm, xshift=4cm](server){Web Server};
\node [block, above of=webapp, yshift=4cm, xshift=-4cm](database){Database};
% Place lines
\path [line](user) edge[bend right] node [right] {user input} (webapp);
\path [line](webapp) edge[bend right] node [left] {app output} (user);
\path [line](webapp) edge[bend right] node [right] {applicaton action} (server);
\path [line](server) edge[bend right] node [left] {action result} (webapp);
\path [line](server) edge[bend right] node [right] {user info request} 
(database);
\path [line](database) edge[bend right] node [left] {user info sent} (server);
\end{tikzpicture}
\caption{Work Context Diagram}
\label{fig:workcontext}
\end{figure}

\subsubsection{Work Partitioning} 
See Table \ref{tab:workpartition}.
\begin{longtable}{|p{5cm}|p{5cm}|p{5cm}|}
\hline
\textbf{Event Name}  & \textbf{Input and Output} & \textbf{Summary} \\ 
\hline
1. User creates account. & \mbox{User Name (IN)} \linebreak \mbox{User ID (IN)} 
\linebreak \mbox{User Password (IN)} \linebreak User Email (IN) & User creates 
an account. The system then adds the account to the database. \\ 
\hline
2. User deletes account. & \mbox{User ID (IN)} \linebreak \mbox{User Password 
(IN)} & User deletes their account. The system then removes the account from the 
database. \\ 
\hline
3. User logs in. & \mbox{User ID (IN)} \linebreak User password (IN) & User logs 
in to app. \\ 
\hline
4. User logs out. & User ID (IN) & User logs out from server. \\
\hline
5. User creates house. & \mbox{User ID (IN)} \linebreak House name (IN) & User 
inputs the house address into system. The system then saves the house in the 
database. \\
\hline
6. User joins house. & \mbox{User ID (IN)} \linebreak House name (IN) & User 
selects a house to join. The system adds the user to the house. \\
\hline
7. User leaves house. & \mbox{User ID (IN)} \linebreak House name (IN) & User 
selects a house to leave. The system removes the user from the house. \\
\hline
8. User uploads file. & \mbox{User ID (IN)} \linebreak File (IN) & User adds a 
file to be visible to house. The system then saves the file in the database 
directory. \\
\hline
9. User submits maintenance request. & \mbox{User ID (IN)} \linebreak 
\mbox{Request (IN)} \linebreak Request (OUT) & User that is tenant submits a 
maintenance request to be received by landlord. \\
\hline
10. User updates maintenance request. & \mbox{User ID (IN)} \linebreak 
\mbox{Request (IN)} \linebreak Request (OUT) & User that is landlord 
\ds{Why can't tenants update maintenance requests?}
completes a 
maintenance request. \\
\hline
11. User adds chore. & \mbox{User ID (IN)} \linebreak \mbox{Chore (IN)} 
\linebreak Calendar (OUT) & User submits a chore to be completed and displayed 
on the Calendar. \\
\hline
12. User initiates chat with other user. & \mbox{User ID (IN)} \linebreak 
\mbox{User ID (IN)} \linebreak Chat (OUT) & User creates chat window with other 
user. \\
\hline
13. User sends instant message. & \mbox{User ID (IN)} \linebreak \mbox{Message 
(IN)} \linebreak Chat (OUT) & User submits a message  and it is displayed 
on the chat window. \\
\hline
14. User adds post. & \mbox{User ID (IN)} \linebreak \mbox{Post (IN)} \linebreak 
Discussion Board (OUT) & User adds post to discussion board. \\
\hline
15. User comments on post. & \mbox{User ID (IN)} \linebreak \mbox{Comment (IN)} 
\linebreak Discussion Board (OUT) & User comments on post on discussion board. 
\\
\hline
16. User transfers funds. & Record of Transaction (OUT) & User transfers funds 
to another user using third-party software. A record of the transaction is 
displayed. \\
\hline
\caption{Work Partitioning}
\label{tab:workpartition}
\end{longtable}
	
\subsection{Business Data Model and Data Dictionary}
N/A.

\subsection{The Scope of the Product}
\subsubsection{Product Boundary}
See Figure \ref{fig:usecase}.
\begin{figure}[H]
\centering
\begin{tikzpicture}[auto, node distance=1cm,>=latex']
% Place nodes  
\node [block2](account){1. Creates Account};
\node [block2, below of=account](delete){2. Deletes Account};
\node [block2, below of=delete](login){3. Login};
\node [block2, below of=login](logout){4. Logout};
\node [block2, below of=logout](create){5. Creates House};
\node [block2, below of=create](join){6. Joins House};
\node [block2, below of=join](leave){7. Leaves House};
\node [block2, below of=leave](upload){8. Uploads File};
\node [block2, below of=upload](submit){9. Submits Maintenance Request};
\node [block2, below of=submit](update){10. Updates Maintenance Request};
\node [block2, below of=update](chore){11. Adds Chore};
\node [block2, below of=chore](chat){12. Initiates Chat};
\node [block2, below of=chat](message){13. Sends Message};
\node [block2, below of=message](post){14. Adds Post};
\node [block2, below of=post](comment){15. Adds Comment};
\node [block2, below of=comment](funds){16. Creates Record of Transaction};
\node [block3, left of=create, xshift=-6cm](lord){Landlord User};
\node [block3, left of=chat, xshift=-6cm](tenant){Tenant User};
\node [block4, right of=create, xshift=6cm](database){Database};
\node [block4, right of=chat, xshift=6cm](server){Web Server};

% Place lines
\draw [arrow] (lord.east) -- (account.west);
\draw [arrow] (lord.east) -- (delete.west);
\draw [arrow] (lord.east) -- (login.west);
\draw [arrow] (lord.east) -- (logout.west);
\draw [arrow] (lord.east) -- (create.west);
\draw [arrow] (lord.east) -- (join.west);
\draw [arrow] (lord.east) -- (leave.west);
\draw [arrow] (lord.east) -- (upload.west);
\draw [arrow] (lord.east) -- (update.west);
\draw [arrow] (lord.east) -- (chore.west);
\draw [arrow] (lord.east) -- (chat.west);
\draw [arrow] (lord.east) -- (message.west);
\draw [arrow] (lord.east) -- (post.west);
\draw [arrow] (lord.east) -- (comment.west);
\draw [arrow] (lord.east) -- (funds.west);

\draw [arrow] (tenant.east) -- (account.west);
\draw [arrow] (tenant.east) -- (delete.west);
\draw [arrow] (tenant.east) -- (login.west);
\draw [arrow] (tenant.east) -- (logout.west);
\draw [arrow] (tenant.east) -- (create.west);
\draw [arrow] (tenant.east) -- (join.west);
\draw [arrow] (tenant.east) -- (leave.west);
\draw [arrow] (tenant.east) -- (upload.west);
\draw [arrow] (tenant.east) -- (submit.west);
\draw [arrow] (tenant.east) -- (chore.west);
\draw [arrow] (tenant.east) -- (chat.west);
\draw [arrow] (tenant.east) -- (message.west);
\draw [arrow] (tenant.east) -- (post.west);
\draw [arrow] (tenant.east) -- (comment.west);
\draw [arrow] (tenant.east) -- (funds.west);

\draw [arrow] (database.west) -- (account.east);
\draw [arrow] (database.west) -- (delete.east);
\draw [arrow] (database.west) -- (login.east);
\draw [arrow] (database.west) -- (logout.east);
\draw [arrow] (database.west) -- (create.east);
\draw [arrow] (database.west) -- (join.east);
\draw [arrow] (database.west) -- (leave.east);
\draw [arrow] (database.west) -- (upload.east);
\draw [arrow] (database.west) -- (submit.east);
\draw [arrow] (database.west) -- (update.east);
\draw [arrow] (database.west) -- (chore.east);
\draw [arrow] (database.west) -- (chat.east);
\draw [arrow] (database.west) -- (message.east);
\draw [arrow] (database.west) -- (post.east);
\draw [arrow] (database.west) -- (comment.east);
\draw [arrow] (database.west) -- (funds.east);

\draw [arrow] (server.west) -- (account.east);
\draw [arrow] (server.west) -- (delete.east);
\draw [arrow] (server.west) -- (login.east);
\draw [arrow] (server.west) -- (logout.east);
\draw [arrow] (server.west) -- (create.east);
\draw [arrow] (server.west) -- (join.east);
\draw [arrow] (server.west) -- (leave.east);
\draw [arrow] (server.west) -- (upload.east);
\draw [arrow] (server.west) -- (submit.east);
\draw [arrow] (server.west) -- (update.east);
\draw [arrow] (server.west) -- (chore.east);
\draw [arrow] (server.west) -- (chat.east);
\draw [arrow] (server.west) -- (message.east);
\draw [arrow] (server.west) -- (post.east);
\draw [arrow] (server.west) -- (comment.east);
\draw [arrow] (server.west) -- (funds.east);

\end{tikzpicture}
\caption{Product Use Case Diagram}
\label{fig:usecase}
\end{figure}

\subsection{Functional and Data Requirements}
\NumTabs{5}
\textbf{Requirement \#:} 1 
      \tab{\textbf{Event/Use Case:} 5} 
      \tab{\textbf{Priority:} 5} \\
      \textbf{Description:} User creates a house within the application. \\
      \textbf{Rationale:} To allow users to self-organize and communicate. \\
      \textbf{Fit Criterion:} A house object is created in the database, with
      the creator as its initial tenant. \\ \\    
\textbf{Requirement \#:} 2 
      \tab{\textbf{Event/Use Case:} 6}
      \tab{\textbf{Priority:} 5} \\
      \textbf{Description:} User joins a house. \\
      \textbf{Rationale:} To allow multiple users to join house groups which
      have already been created. \\
      \textbf{Fit Criterion:} The user is added to the list of tenants
      associated with the house they are joining. \\ \\
\textbf{Requirement \#:} 3 
      \tab{\textbf{Event/Use Case:} 8}
      \tab{\textbf{Priority:} 3} \\
      \textbf{Description:} User uploads a file. \\
      \textbf{Rationale:} To allow users to share documents. \\
      \textbf{Fit Criterion:} The file that is uploaded is added to the set of
      files associated with that house. \\ \\
\textbf{Requirement \#:} 4
      \tab{\textbf{Event/Use Case:} 8}
      \tab{\textbf{Priority:} 3} \\
      \textbf{Description:} User downloads a file. \\
      \textbf{Rationale:} To allow users to retrieve and save documents that 
have
      been uploaded by other users in their house. \\
      \textbf{Fit Criterion:} The file selected by the user is downloaded to
      their machine. \\ \\
\textbf{Requirement \#:} 
      \tab{\textbf{Event/Use Case:}}
      \tab{\textbf{Priority:} } \\
      \textbf{Description:} Landlords and tenants shall communicate through a discussion
    board. \\
      \textbf{Rationale:} Landlords and tenants will not need to communicate via email,
    text message, or phone. \\
      \textbf{Fit Criterion:} All communications conducted via the product's discussion
    board will be instant and accessible by all members of the group. \\ \\ 
\textbf{Requirement \#:} 5
      \tab{\textbf{Event/Use Case:}}
      \tab{\textbf{Priority:} 2} \\
      \textbf{Description:} Users shall be able to specify which other users
      are able to view content that they post or uploaded. \\
      \textbf{Rationale:} To allow users to share content and communicate
      privately and keep sensitive data safe. \\
      \textbf{Fit Criterion:} Content shall only be visible to those who the
      creator has specified are able to view it. \\ \\
\textbf{Requirement \#:} 6
      \tab{\textbf{Event/Use Case:} 9}
      \tab{\textbf{Priority:} 4} \\
      \textbf{Description:} Tenants shall be able to create maintenance
      requests. \\
      \textbf{Rationale:} To allow tenants to inform their landlord of property
      related work that needs to be addressed in a structured manner, as opposed to random messages via email, text or phone.\\
      \textbf{Fit Criterion:} Landlords shall be able to view a list of current
      maintenance requests as soon as they are created by their tenants.\\ \\          
\textbf{Requirement \#:} 7
      \tab{\textbf{Event/Use Case:} 3}
      \tab{\textbf{Priority:} 5} \\
      \textbf{Description: }{User login.} \\
      \textbf{Rationale: }{All users should be able to securely login.} \\
      \textbf{Fit Criterion: }{Upon passing proper credentials, user completes 
the login process.} \\ \\
\textbf{Requirement \#:} 8
      \tab{\textbf{Event/Use Case:} 1}
      \tab{\textbf{Priority:} 4} \\
      \textbf{Description: }{Account registration.} \\
      \textbf{Rationale: }{Potential users may register an account using 
Facebook, Google Plus, or registering with Quarters directly.} \\
      \textbf{Fit Criterion: }{Registering should be a one-step process, with 
email verification to confirm identity.} \\ \\        
\textbf{Requirement \#:} 9
      \tab{\textbf{Event/Use Case:} 14,15} 
      \tab{\textbf{Priority:} 4}\\
      \textbf{Description: }{Bulletin board.} \\
      \textbf{Rationale: }{Users are able to post and view information, and 
comment on other posts to enhance communications.} \\
      \textbf{Fit Criterion: }{Posts on the bulletin should be sorted 
chronologically, and viewable by the designated user.} \\ \\        
\textbf{Requirement \#:} 10
      \tab{\textbf{Event/Use Case:}
      \tab{\textbf{Priority:} 5} \\
      \textbf{Description: }{Multiple resolution compatibility.} \\
      \textbf{Rationale: }{Users may have different devices with different 
screen resolutions. The application should be able to support all types.} \\
      \textbf{Fit Criterion: }{Web platform should support mobile screens and 
desktop screens, including both horizontal and vertical layouts.} \\ \\        
\textbf{Requirement \#:} 11
      \tab{\textbf{Event/Use Case:} 6}
      \tab{\textbf{Priority:} 5} \\
      \textbf{Description: }{House management.} \\
      \textbf{Rationale: }{Administrator should be able to determine which users 
can access the house.} \\
      \textbf{Fit Criterion: }{Administrators can add, edit and remove users 
from a house.} 
\ds{Who are the administrators? Are they developers of ``Quarters" or landlords?}
\\ \\        
\textbf{Requirement \#:} 12
      \tab{\textbf{Event/Use Case:} 16}
      \tab{\textbf{Priority:} 3} \\
      \textbf{Description: }{Financial platform.} \\
      \textbf{Rationale: }{Payments between users may be processed within the 
platform to discard cash handling or the use of post-dated cheques.} \\
      \textbf{Fit Criterion: }{Payments are secure and logged. Payer and payee 
will be notified upon payment completion.} \\ \\        
\textbf{Requirement \#:} 13
      \tab{\textbf{Event/Use Case:} 11}
      \tab{\textbf{Priority:} 3} \\
      \textbf{Description: }{Calendar platform.} \\
      \textbf{Rationale: }{Events tied to the house can be made in the calendar 
platform. Chores and other repeating events can be created here.} \\
      \textbf{Fit Criterion: }{Calendar format should be based off the 
standardized ICS structure. This format should be deployable to other calendar 
management software. This platform should support the creation, deletion and 
modifications to an event.} \\ \\
\ds{How does a landlord end up on a house?}
\ds{You have not covered the entirety of your use cases. Where are the rest of
	your requirements?}
        
\section{Nonfunctional Requirements}
\subsection{Look and Feel Requirements}
\subsubsection{Appearance Requirements}
The interface of the web application shall be attractive and intuitive for a 
young adult and adult audience.

\subsubsection{Style Requirements}
The web application shall appear professional and secure.

\subsection{Usability and Humanity Requirements}
\subsubsection{Ease of Use Requirements}
The 
web application shall be used by users with no prior training. A casual user should 
be able to use the application with the same ease of a frequent user. The 
application shall make the users want to use it. A test panel of current 
landlords and their tenants shall be able to successfully create a user account 
and use the application's functions without guidance within their first 
encounter.
\subsubsection{Personalization and Internationalization Requirements}
The web application shall be available in the Canadian English language (EN-CA),  use 
Canadian currency (CAD \$), ICS Calendar format, and the metric system.
\subsubsection{Learning Requirements}
The web application shall be easy to learn for users 18 years of age or older. The web 
application shall be constructed so that all of its functionality is apparent 
upon first encountering it. A brief tour of the web application shall be 
presented as an option to first time visitors of the site. A test panel of 
current landlords and their tenants shall be able to successfully create a user 
account and use the application's functions productively without guidance within 
their first encounter.
\subsubsection{Understandability and Politeness Requirements}
The web application shall use symbols, icons, and words that users have seen and used before on other web applications.
\subsubsection{Accessibility Requirements}
N/A.
\subsection{Performance Requirements}
\subsubsection{Speed and Latency Requirements}
N/A.
\subsubsection{Safety-Critical Requirements}
N/A.
\subsubsection{Precision or Accuracy Requirements}
The web application shall keep accurate time by working in UTC. All monetary 
amounts shall be accurate to two decimal places. 
\subsubsection{Reliability and Availability Requirements}
The web application shall be available for use 24 hours per day, 365 days per 
year.
\subsubsection{Robustness or Fault-Tolerance Requirements}
The web application shall successfully display an error message to the user 
should an incorrect username/password combination be input, or in the event one of its features crashes.  
\ds{There should be error-related functional requirements as well. When the
error message occurs, what happens? Does the program stop or can the user 
continue performing tasks?}
\subsubsection{Capacity Requirements}
The web application shall cater to 100 simultaneous users during its initial release. Capacity will increase with expansion.
\subsubsection{Scalability or Extensibility Requirements}
The web application shall be capable of expanding to nearby cities within two 
years of its launch.
\subsubsection{Longevity Requirements}
The web application shall be expected to operate as long as there exists a 
housing rental market.
\subsection{Operational and Environmental Requirements}
\subsubsection{Expected Physical Environment}
N/A.
\subsubsection{Requirements for Interfacing with Adjacent Systems}
The web application shall work on the last three releases of the five most 
popular web browsers (Chrome, Firefox, Internet Explorer, Opera, Safari). The 
web application shall interface with PayPal to handle monetary transactions 
between users. The web application shall interface with Google Sign-In and 
Facebook Login to enable users to login with social media accounts. The details 
of the communication standards/protocols will be outlined in the Design Document 
after implementation is completed.
\subsubsection{Productization Requirements}
The web application shall be accessible on the World Wide Web.
\subsubsection{Release Requirements}
The initial release of the web application will be in February 2016. The next 
release will be in April 2016.
\subsection{Maintainability and Support Requirements}
\subsubsection{Maintenance Requirements}
The web application shall be able to be maintained by developers who are not the 
original developers.
\ds{That is not a good requirement.}
\subsubsection{Supportability Requirements}
N/A. 
\ds{You may want to include supportability requirements}

\subsubsection{Adaptability Requirements}
The web application is expected to run on web browsers on mobile phones, tablets 
and desktop computers.
\subsection{Security Requirements}
\subsubsection{Access Requirements}
Only the user has access to edit their own personal stored information and 
choose what information of their profile is visible to other users. Users have 
access to view other users' profiles. Only the landlords and tenants belonging 
to the same property can view the property's group and add content to the 
property's group.
\subsubsection{Integrity Requirements}
The web application shall prevent incorrect data from being introduced and 
protect itself from unwanted attacks by unauthorized users. The web application 
shall have a back-up of its stored data on an alternate server.
\subsubsection{Privacy Requirements}
The web application shall make its users aware of its information practices 
before collecting data from them. The web application shall authorize account 
registration of users using social media accounts. The web application shall use 
a third-party interface to store credit card information and perform secure 
monetary transactions between users.

\ds{Is data stored securely? Is it tamper-proof?}
\subsubsection{Audit Requirements}
N/A.
\subsubsection{Immunity Requirements}
N/A.
\subsection{Cultural and Political Requirements}
\subsubsection{Cultural Requirements}
N/A.
\subsection{Legal Requirements}
\subsubsection{Compliance Requirements}
N/A.
\subsubsection{Standards Requirements}
N/A.

\section{Project Issues}
\subsection{Open Issues}
\begin{itemize}
  \item Size of the user group is uncertain, therefore a hardware upgrade may be 
required in the future to accommodate the user.
  \item User interface has yet to be designed.
  \item Browser compatibility.
  \item Methods to store documents, eg. database vs locally on server
\end{itemize}

\subsection{Off the Shelf Solutions}
\subsubsection{Ready-Made Products}
No ready-made products exist with the same functionalities. 
\subsubsection{Reusable Components}
Facebook and Google accounts can be used for sign-in and connecting members in 
the house.
\subsubsection{Products That Can Be Copied}
N/A
\subsection{New Problems}
\subsubsection{Effects on the Current Environment}
N/A
\subsubsection{Effects on the Installed Systems}
N/A
\subsubsection{Potential User Problems}
N/A
\subsubsection{Limitations in the anticipated Implementation environment That 
May Inhibit the New Product}
Old browsers are not compatible with the product.
\subsubsection{Follow-Up Problems}
\begin{itemize}
  \item User abusing the system.
  \item User uploading sensitive data.
\end{itemize}

\subsection{Tasks}
\subsubsection{Project Planning}
\begin{itemize}
  \item Present requirement document to supervisor for feedback.
  \item Develop prototype for demo purpose
  \item Refine and develop more features.
\end{itemize}
\subsubsection{Planning of the Development Phases}
\begin{itemize}
    \item Design the database together.
    \item Design a generalized UI.
    \item Design back-end of the application.
    \item Split application into different modules and assign one module to each 
member for completion.
    
\end{itemize}
\subsection{Migration to New Product}
N/A
\subsubsection{Requirements for Migration to the New Product}
N/A
\subsubsection{Data That has to be Modified or Translated for the New System}
N/A
\subsection{Risks}
\begin{itemize}
  \item Security/legal issues with online payment.
  \item Not able to get enough users.
  \item Certain features may not be compatible with the hardware.
  \item Project becomes too complicated and not able to meet deadlines.
\end{itemize}
\subsection{Costs}
\begin{itemize}
  \item Domain costs and web server costs, if we decide to go live.
  \item Approximately 7 months of development time.
\end{itemize}
\subsection{User Documentation and Training}
\subsubsection{User Documentation Requirements}
\begin{itemize}
  \item A help guide will be included.
  \item FAQ section.
  \item Tour of the website is shown for first time user.
\end{itemize}
\subsubsection{Training Requirements}
No training is required for the user. When they visit for the first time they 
will be given a tour. 
\subsection{Waiting Room}
The next release will include the following features:
\begin{itemize}
	\item Separate module for housing advertisements.
	\item Ability to attach pictures and files in discussion board.
	\item Notifications either through email or text messages (for urgent events).
\end{itemize}
\subsection{Ideas for Solutions}
\begin{itemize}
  \item PostgreSQL for database management.
  \item NodeJS and ExpressJS for server side.
  \item AngularJS and Bootstrap for front end.
\end{itemize}
\ds{Are these ideas for solutions or constraints? You put them in both places.}

\end{document}

